---
title: 'A3: Team Project - Marketing SF'
author: Team 12 - Yash Maradia, Khizer Sultan, Pablo Ramirez, Shimon Takahashi, Paolo
  Musone
date: "14/11/2021"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
```


```{r data, echo=FALSE, message=FALSE, warning=FALSE}

library(readxl)
datasets_marketing_campaign_SF_1_ <- read_excel("C:/Users/ramir/Desktop/MBA/HULT/Courses/MBAN/Data Science with R/datasets_marketing_campaign_SF (1).xlsx")
View(datasets_marketing_campaign_SF_1_)
sf <- datasets_marketing_campaign_SF_1_


#install.packages("ggplot2")a

#install.packages("plotly")

library(ggplot2)
library(plotly)

```


```{r message=FALSE, warning=FALSE, include=FALSE}
#Exploring if there are any "NA" elements in the data set... 34 NA elements in the data set= 1,5% of the total data#
is.na(sf)
which(is.na(sf))

#Cancel the 34 NA elements from the dataset.
sf<-na.omit(sf)

#Replace each variable from Education column to a numeric variable#
sf$Education <- gsub("PhD","0", sf$Education)
sf$Education <- gsub("Master","1", sf$Education)
sf$Education <- gsub("Graduation", "2", sf$Education)
sf$Education <- gsub("2n Cycle", "3", sf$Education)
sf$Education <- gsub("Basic", "4", sf$Education)
sf$Education <- as.numeric(sf$Education)
print(sf$Education)

#Replace each variable from Marital_Status  column to a numeric variable#
sf$Marital_Status <- gsub("Widow", "0", sf$Marital_Status)
sf$Marital_Status <- gsub("Single", "1", sf$Marital_Status)
sf$Marital_Status <- gsub("Divorced", "2", sf$Marital_Status)
sf$Marital_Status <- gsub("Married", "3", sf$Marital_Status)
sf$Marital_Status <- gsub("Together", "4", sf$Marital_Status)
sf$Marital_Status <- gsub("Alone", "5", sf$Marital_Status)
sf$Marital_Status <- gsub("Absurd", "6", sf$Marital_Status)
sf$Marital_Status <- gsub("YOLO", "7", sf$Marital_Status)
sf$Marital_Status <- as.numeric(sf$Marital_Status)
print(sf$Marital_Status)

#Replace each variable from Country column to a numeric variable#
sf$Country <- gsub("AUS", "0", sf$Country)
sf$Country <- gsub("US", "1", sf$Country)
sf$Country <- gsub("CA", "2", sf$Country)
sf$Country <- gsub("GER", "3", sf$Country)
sf$Country <- gsub("IND", "4", sf$Country)
sf$Country <- gsub("ME", "5", sf$Country)
sf$Country <- gsub("SA", "6", sf$Country)
sf$Country <- gsub("SP", "7", sf$Country)
sf$Country<- as.numeric(sf$Country)
print(sf$Country)

#Modifying dates#

#Converting Dt_customer in as.date format
sf$Dt_Customer<- as.Date(sf$Dt_Customer)

#creating a "Today Variable" and converting in as.date format
sf$Year_2014 <- c()
for(i in 1:nrow(sf)){
 sf$Year_2014[1] <-("2014-12-31") 
}
sf$Year_2014<-as.Date(sf$Year_2014)

#Exploring the Age variable#
summary(sf$Age)


# Creating new variables #

# Total purchases #
sf$Total_Purchases<- sf$NumDealsPurchases+sf$NumWebPurchases+sf$NumCatalogPurchases+sf$NumStorePurchases

# Customers Age #
sf$Age<-2015 - sf$Year_Birth

# How many days are the customers enrolled in the Retailer subscription #
sf$days_of_Subscription<- (sf$Year_2014 - sf$Dt_Customer)

```



# Q1: The variables that drive Web purchases are: Income, Number of Web visits each month, Amount spent on Wines, Amount spend on Fish products and how many teens does the customer has, if any...
```{r Part 1 - a, echo=FALSE, message=FALSE, warning=FALSE}
############ Part 1 - a: Variables that impact most "NumWebPurchases" and CMO recommendations ###########
# Q1: What variables drive Web purchases #
# Total purchases #
sf$Total_Purchases<- sf$NumDealsPurchases+sf$NumWebPurchases+sf$NumCatalogPurchases+sf$NumStorePurchases

sf$Age<-2015 - sf$Year_Birth

# How many days are the customers enrolled in the Retailer subscription #
sf$days_of_Subscription<- (sf$Year_2014 - sf$Dt_Customer)

# Creating new variables for regression purposes #
sf$binary_Education <- c()
for(i in 1: nrow(sf)){
  if(sf$NumWebPurchases[i]>0 ){
    sf$binary_Education[i]<-"1"
  }else{
    sf$binary_Education[i]<-"0"
  }#closing my if statement 
}# closing the i loop

sf$binary_Education<-as.numeric(sf$binary_Education)

sf$binary_Marital_Status <- c()
for(i in 1: nrow(sf)){
  if(sf$Marital_Status[i]==3 & 4){
    sf$binary_Marital_Status[i] <- "1"
  }else{
    sf$binary_Marital_Status[i]<- "0"
  }#closing my if statement
}# closing the i loop
sf$binary_Marital_Status<-as.numeric(sf$binary_Marital_Status)

# Data Frame with all the numeric data#
Numeric_data<- as.data.frame(sf[c( "binary_Education","binary_Marital_Status","Income","Kidhome","Teenhome","Recency","MntWines",
                                   "MntFruits", "MntMeatProducts","MntFishProducts","MntSweetProducts","MntGoldProds", "NumDealsPurchases",
                                   "NumCatalogPurchases","NumStorePurchases" ,"NumWebVisitsMonth","NumWebPurchases","AcceptedCmp3", "AcceptedCmp4" , "AcceptedCmp5",
                                   "AcceptedCmp1", "AcceptedCmp2","Complain" , "Response" ,"Total_Purchases",
                                   "Age","Z_CostContact","Z_Revenue")])


#Train 80% of "Numeric_data" and test them with the outstanding 20% of the data#
train_index <- sample(1:nrow(Numeric_data),size= 0.8*nrow(Numeric_data))
sf_train <- Numeric_data[train_index,]
sf_test <- Numeric_data[-train_index,]

#Linear regression using the trained data#

#The regression is clearly over fitted with unsignificant variables, which will be removed later to perform our linear regression analysis
LR<-lm(NumWebPurchases~Income+Kidhome+Teenhome+Recency+MntWines+
         MntFruits+ MntMeatProducts+MntFishProducts+MntSweetProducts+MntGoldProds+NumDealsPurchases+
         NumCatalogPurchases+NumStorePurchases+NumWebVisitsMonth+AcceptedCmp3+ AcceptedCmp4+ AcceptedCmp5+
         AcceptedCmp1+ AcceptedCmp2+Complain+Response+Total_Purchases+
         Age+binary_Education+binary_Marital_Status, data=sf_train)
summary(LR)

LR_significant <- lm(NumWebPurchases~Income+Kidhome+Teenhome+MntWines+
                      MntFishProducts+NumWebVisitsMonth, data=sf_train)
summary(LR_significant)

#Data Normalization
min_max_norm <- function(Numeric_data) {
  ( Numeric_data- min(Numeric_data)) / (max(Numeric_data) - min(Numeric_data))
}

#apply Min-Max normalization to the data set
Normalized_data <- as.data.frame(lapply(Numeric_data, min_max_norm))

train_index1 <- sample(1:nrow(Normalized_data),size= 0.8*nrow(Normalized_data))
sf_train_norm <-Normalized_data[train_index,]
sf_test_norm <- Normalized_data[-train_index,]

#Linear Regression of Normalized data for comparing the estimated slopes among the significant variables#
LR_significant_norm<-lm(NumWebPurchases~Income+Kidhome+Teenhome+MntWines+
                           MntFishProducts+NumWebVisitsMonth, data=sf_train_norm)
summary(LR_significant_norm)

```

# Part 1 - b: Only 11.52% of the data from Rest of the World (RoW) can be explained because of the purchases that people make in USA, which is not very significant / impactful on our data.

```{r Part 1 - b, echo=FALSE, message=FALSE, warning=FALSE}
#for usa
sf$Usa_total_purchase <- c()
for(i in 1: nrow(sf)){
  
  if(sf$Country[i]==1 ){
    sf$Usa_total_purchase[i]<-sf$Total_Purchases[i]
  }else{
    sf$Usa_total_purchase[i]<- 0
  }#closing my if statement 
}# closing the i loop
sum(sf$Usa_total_purchase)


#for rest of the world
sf$RoW_total_purchase <- c()
for(i in 1: nrow(sf)){
  
  if(sf$Country[i] !=1 ){
    sf$RoW_total_purchase[i]<-sf$Total_Purchases[i]
  }else{
    sf$RoW_total_purchase[i]<- 0
  }#closing my if statement 
}# closing the i loop
sum(sf$RoW_total_purchase)

train_index <- sample(1:nrow(sf), size=0.8*nrow(sf))

SF_train_3 <- sf[train_index,]
SF_test_3 <- sf[-train_index,]

linear_model <- lm(Usa_total_purchase ~ RoW_total_purchase
                   ,data=SF_train_3)

summary(linear_model)

linear_model_2 <- lm(Usa_total_purchase ~ RoW_total_purchase
                     ,data=SF_test_3)

summary(linear_model_2)

cor(SF_train_3$Usa_total_purchase, SF_train_3$RoW_total_purchase)

Usa_perCapita <- sum(sf$Usa_total_purchase)/sum(sf$Country==1)
RoW_perCapita <- sum(sf$RoW_total_purchase)/sum(sf$Country==0)
Usa_perCapita
RoW_perCapita

```

# Part 1 - c: There is not enough evidence to confidently conclude that people who spend above the average amount on gold would have more store purchases.

```{r Part 1 - c, echo=FALSE, message=FALSE, warning=FALSE}
#Exploring the MntGoldProds data#
hist(sf$MntGoldProds)
#People spend an average of USD $43.96 in gold#
Gold_Mean <- mean(sf$MntGoldProds)
summary(sf$MntGoldProds)

#Creating a Dummy variable for people who spend in Gold above USD $43.96 = "1" and below = "0"#
sf$DummyGold_Above_Mean <- c()
for(i in 1: nrow(sf)){
  if(sf$MntGoldProds[i] > 43.96){
    sf$DummyGold_Above_Mean[i] <- 1
  }else{
    sf$DummyGold_Above_Mean[i] <- 0
  }#closing my if statement 
}# closing the i loop
sum(sf$DummyGold_Above_Mean)

####### Logistic Regression: DummyGold_Above_Mean VS NumStorePurchases##########

DummyGold_Above_Mean_VS_StorePurchases_logreg <- glm(DummyGold_Above_Mean~NumStorePurchases, data = sf, family = "binomial")
summary(DummyGold_Above_Mean_VS_StorePurchases_logreg)

####### Linear Regression: MntGoldProds VS NumStorePurchases ##########

Gold_VS_StorePurchases_linear <- lm(MntGoldProds~NumStorePurchases, data=sf)
summary(Gold_VS_StorePurchases_linear)

plot(x = sf$MntGoldProds, y = sf$NumStorePurchases)

```


# Part 1 - d: There is a significant relation between married and PhD customers with amount spend on fish.  As we can see from the graph the number of people who are married and has a PhD degree are “good” and the rest others are “bad”.

```{r Part 1 - d, echo=FALSE, message=FALSE, warning=FALSE}
sf$Married_PhD<- c()
for(i in 1: nrow(sf)){
  if(sf$Marital_Status[i] == 3 & sf$Education[i] == 0){
    sf$Married_PhD[i] <- "good"
  }else{
    sf$Married_PhD[i] <- "bad"
  }#closing my if statement 
}# closing the i loop

linearMod <- lm(`MntFishProducts`~ .,
                data = sf)
summary(linearMod)

linearMod2<-  lm(`MntFishProducts`~ sf$Married_PhD,
                 data = sf)
summary(linearMod2)

library(ggplot2)

ggplot(data=sf, aes(x=sf$`MntFishProducts`, y=sf$Married_PhD)) + geom_jitter()

```

# Q7 - Teenagers spend most on Wines... but Meat is the most consumed food #

```{r Part 1 - e Q7, echo=FALSE, message=FALSE, warning=FALSE}

#Pie Chart with Percentages for families with teens product consumption# 
slices <- c(325143, 20159, 110127, 27418, 21414, 45682)
lbls <- c("Wine", "Fruit", "Meat", "Fish", "Sweet", "Gold")
pct <- round(slices/sum(slices)*100)
lbls <- paste(lbls, pct) # add percents to labels
lbls <- paste(lbls,"%",sep="") # ad % to labels
pie(slices,labels = lbls, col=rainbow(length(lbls)),
    main="Product consumption by families with Teenagers")
```

# Q8 - Campaign #4 is the most successful, followed by campaign #3 and #5 which had very similar performance and results. 

```{r Part 1 - e Q8, echo=FALSE, message=FALSE, warning=FALSE}

#Most succesfull Campaign is determined by the sum of successes in each Campaign... "AcceptedCmp4" is the most succesfull with 164 successes (purchases)#
Campaign1_successes <- sum(sf$AcceptedCmp1)
Campaign2_successes <- sum(sf$AcceptedCmp2)
Campaign3_successes <- sum(sf$AcceptedCmp3)
Campaign4_successes <- sum(sf$AcceptedCmp4)
Campaign5_successes <- sum(sf$AcceptedCmp5)

#Most efficient Campaign is determined by dividing the amount of successes by total observations or attempts#
sum(sf$AcceptedCmp1)/2240*100
sum(sf$AcceptedCmp2)/2240*100
sum(sf$AcceptedCmp3)/2240*100
sum(sf$AcceptedCmp4)/2240*100
sum(sf$AcceptedCmp5)/2240*100

success <- c(sum(sf$AcceptedCmp1)/2240*100,
             sum(sf$AcceptedCmp2)/2240*100,
             sum(sf$AcceptedCmp3)/2240*100,
             sum(sf$AcceptedCmp4)/2240*100,
             sum(sf$AcceptedCmp5)/2240*100)

campagins <- c(1,2,3,4,5)

as.data.frame(success)
as.data.frame(campagins)

new_df <- cbind.data.frame(success,campagins)

ggplot(data= new_df, aes(x= campagins,y = success))+
  geom_bar(stat = "identity", fill = "#FF6666")
theme(axis.text.x = element_text(angle = 45, hjust = 1))



```
